---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  eval = FALSE
)
```



# Quick SpideR

## Setup

```{r}
library(SpideR)
startSpideR(dir=getwd()) # The 'dir' argument determines the location of large database files
```



## Search for (unknown) experiments - by search terms

```{r}
searchForTerm(library_strategy = "ChIP-Seq", antibody = c("p53", "tp53"), species = c("9606", "10090"))
```


## Search for (known) experiments - by accession numbers

```{r}
searchForAccession("SRP010068")
```


## Convert between accession types

```{r}
df <- convertAccession("SRP010068")
```


---

# SpideR Overview

- what is SpideR for?
- what are the requirements for using it?



# SpideR Setup

- Requirements (time and space)

# Tasks

- Search for unknown experiments by search terms
- Search for known experiments by their accession number
- Convert between accession types
- Repeat SpideR query from the past (NOTE: db might have changed etc.)


https://www.ncbi.nlm.nih.gov/taxonomy 
