---
title: "Quick SpideR"
author: "AS"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


Quick SpideR - a cheat sheet with rapid intro to SpideR package.


# Why SpideR?
SpideR allows for search and retrieval of data from SRA and GEO databases.  



# Setup
In order to use SpideR, please ensure that you have the following installed:

- R
- SpideR
- SRAdb
- GEOmetadb
- any additional package dependencies (as prompted during SpideR installation process)


You must run the following in order to start using SpideR (this should be done every time a new session is commenced).  

```{r, eval = FALSE}
library(SpideR)
startSpideR(dir=getwd()) # The 'dir' argument determines the location of large database files (running this command for the first time can be time consuming, but will be fast on all successive runs provided that the directory does not change)
```


# SpideR by Task
For more detailed information, please refer to the main package vignette.  

The subsections below introduce typical tasks and examples of how they can be completed using main SpideR functions.  


## Search for (unknown) experiments - by search terms (searchForTerm)

**TASK:** *"I would like to find the ChIP-Seq experiments that were done about p53 on human and mouse systems."*  
```{r, eval = FALSE}
searchForTerm(library_strategy = "ChIP-Seq", antibody = c("p53", "tp53"), species = c("9606", "10090"))
```



## Search for (known) experiments - by accession numbers (searchForAccession)

**TASK:** *"I would like to retrieve a handy list of samples from a study I already know."*  
```{r, eval = FALSE}
searchForAccession("SRP010068")
```


## Convert between accession types (convertAccession)
**TASK:** *"I have a study accession number and would like to find a list of sample accessions that belong to it."*  
```{r, eval = FALSE}
df <- convertAccession("SRP010068") 
```

Note that, unlike in the examples above, here we save the result to a data frame (the functions above generated output files on your computer).  
<br>


**TASK:** *"I would like to convert a list of accessions in SRA to accessions in GEO."*  
```{r, eval = FALSE}
x <- c("SRR7348421", "SRR7348425", "SRR7348430")
df <- convertAccession(x)
```



## Find out more about the databases (getDatabaseInformation)

**TASK:** *"I would like to know what are the experiment types (library_strategy) featured in the database."*
```{r, eval = FALSE}
getDatabaseInformation() #choose a relevant option from the menu when it appears
```


