---
title: "SpideR Guide"
author: "AS"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Sources of Documentation

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

This vignette aims to provide the most comprehensive piece of documentation on the SpideR package.  
<br>
For quick reference, please refer to Quick_SpideR vignette.  
<br>
Package documentation can also be viewed via help pages, i.e.  
```{r}
#Main page of package documentation
package?SpideR

# Documentation for individual functions
?searchForTerm
?searchForAccession
#etc.
```


# SpideR Overview

SpideR allows for search and retrieval of data from SRA and GEO databases.  
Its aim is to provide a more unified framework to access these two databases, integrate information between them and allow efficient and convenient retrieval of the data.  
It can be used in a variety of ways including tasks such as:  

- Searching for experiments that were done about X  
- Searching for experiments based on their accession number  
- Converting between accession numbers  

# Requirements

SpideR relies on the SRAdb and GEOmetadb packages. They provide large database files (at the time of writing about 40 GB in total).  
The user can specify the location of these files when running startSpideR(dir="Path_To_Folder_Of_Interest").  

<br>
In general, the requirements for running SpideR include:  

- R (we recommend to use it via RStudio)  
- dependency R packages (as per DESCRIPTION file), including:  
    * SRAdb  
    * GEOmetadb 
    * **NOTE:** these two need to be installed manually via Bioconductor  
- at least 40 GB of free disc space  


# Setup

1. Before proceeding, please ensure that you have the following packages installed (they are distributed via Bioconductor):

- SRAdb
- GEOmetadb

2. Install SpideR.

Under the development version ===*===, this is done by downloading the SpideR directory, opening a session in that directory and running:
```{r}
devtools::load_all()
```


3. Initialise SpideR.

This has to be done every time you want to use SpideR in a new session.

```{r}
startSpideR(dir=getwd()) # dir specifies the location where database files will be stored
```


It may take a considerable amount of time the first time it is run. This is due to the need for downloading large database files and creating an extra custom database.  
However, once these are in place, the above command should take a matter of seconds or less.  

# SpideR by Functions

## Brief Overview

1. searchForTerm - search for (unknown) experiments matching search terms of interest
2. searchForAccession - search for (known) experiments which match the accession numbers
3. accessionConverter - convert between SRA and/or GEO accessions
4. reproduceResults / rerunQuery ===*=== - run again a SpideR query from the past (NB: the results might differ if the database changed)
5. getDatabaseInformation - get basic information about the databases





-------



https://www.ncbi.nlm.nih.gov/taxonomy 